Using Sorghum as an outgroup to find syntenic regions in Maize: regenerating

### 2017-10-13 SubGenome Analysis.Rmd
Examining correlations

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```

@@

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```
# Wrapup
***
Report generated on: `r as.character(format(Sys.Date(), format="%B %d, %Y"))`

>>>>

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of expression for gene pair(s).\nAlpha=.1, reference line"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Expression for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```

@@

plot <-
  ggplot(data, aes(x=Value_maize1, y=Value_maize2)) +
  geom_point(alpha=.1, aes(color = Sample)) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  labs(
    title = paste0("Scatterplot of protein abundance for gene pair(s).\nAlpha=.1, reference line"),
    x = "Abundance for Maize1 Gene (log scale)",
    y = "Abundance for Maize2 Gene (log scale)"
  ) +
  theme(legend.position = "none") + facet_wrap(~Sample, nrow=6)
plot(plot)
```

# Expression and Abundance are Weakly Correlated

```{r subgenome_expression_protein_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=8, fig.height=8, fig.align='center'}
## Start with the paired expression data
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.expression.sample.avg, by=c("Maize1"="geneID")) %>%
  inner_join(maize.expression.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

## Add paired abundance data
data <-
  data %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize1"="geneID", "Sample"="Sample")) %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[6] <- "dNSAF_maize1"
names(data)[7] <- "dNSAF_maize2"

## View as scatter
ggplot(data, aes(FPKM_maize1, dNSAF_maize1)) +
  geom_point(alpha=.1) +
  geom_smooth(method="loess", se=TRUE, fullrange=FALSE, level=0.95) +
  geom_abline(mapping = null, data = null, slope = 1, intercept = 0) +
  scale_x_log10() + scale_y_log10() +
  facet_wrap(~Sample, nrow=6) +
  labs(
    title = paste0("Scatterplot of Expression in Maize1 vs. Abundance in Maize1\nLog-Log Scale for gene pair(s).\nAlpha=.1, reference line (black), loess fit (blue)"),
    x = "Expression for Maize1 Gene (log scale)",
    y = "Abundance for Maize1 Gene (log scale)"
  ) 
```

```{r subgenome_expression_protein_foldchange_scatter, echo=FALSE, warning=FALSE, message=FALSE, results='asis', fig.width=6, fig.height=5, fig.align='center'}
## Start with the paired expression data
data <-
  homeologs.pairs %>%
  subset(Maize1 != "" & Maize2 != "") %>%
  select(Maize1, Maize2) %>%
  distinct() %>%
  inner_join(maize.expression.sample.avg, by=c("Maize1"="geneID")) %>%
  inner_join(maize.expression.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(FPKM_avg.x) & !is.na(FPKM_avg.y))
names(data)[4] <- "FPKM_maize1"
names(data)[5] <- "FPKM_maize2"

## Add paired abundance data
data <-
  data %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize1"="geneID", "Sample"="Sample")) %>%
  inner_join(maize.protein.abundance.sample.avg, by=c("Maize2"="geneID", "Sample"="Sample")) %>%
  subset(!is.na(dNSAF_avg.x) & !is.na(dNSAF_avg.y))
names(data)[6] <- "dNSAF_maize1"
names(data)[7] <- "dNSAF_maize2"

data$foldChange_expr <- log2(data$FPKM_maize1) - log2(data$FPKM_maize2)
data$foldChange_abun <- log2(data$dNSAF_maize1) - log2(data$dNSAF_maize2)
ggplot(data, aes(foldChange_expr, foldChange_abun)) +
  geom_point(alpha=.1) +
  xlim(-10,10) + ylim(-10,10) +
  geom_smooth(method="lm", se=TRUE, fullrange=FALSE, level=0.95) +
  # facet_wrap(~Sample, nrow=6) +
  labs(
    title = paste0("Scatterplot of Foldchange in Expression in Maize1 vs.\nFoldchange in Abundance in Maize1\nAlpha=.1, linear fit, n=13413"),
    x = "log2(Expression Maize1) - log2(Expression Maize2)",
    y = "log2(Abundance Maize1) - log2(Abundance Maize2)"
  ) + 
  annotate("text",x=7,y=-8, label=paste("Pearson Cor = ", round(cor(data$foldChange_expr, data$foldChange_abun, method = c("pearson")),2)))
```

# Wrapup
***
Report generated on: `r as.character(format(Sys.Date(), format="%B %d, %Y"))`
